divan: An R Shiny app for exploratory functional diversity analyses

### 2023-11-17 paper/paper.Rmd
update ms

![Figure 1. The graphical user interface (GUI) of **divan** after loading a community matrix. (a) Sidebar menu, (b) heatmap plus dendrogram of the community matrix, (c) rarefaction curves of individual sites. \label{fig:fig1}](../fig/fig_1.jpg)

@@

![Figure 2. The GUI of divan after loading a trait matrix. (a) Sidebar menu, (b) selection of functional traits for analysis and plotting, (c) Principal Coordinate Analysis (PCoA) inputs, (d) biplot of species and functional traits plus density kernel surface.\label{fig:fig2}](../fig/fig_2.jpg)

@@

>>>>

![The graphical user interface (GUI) of **divan** after loading a community matrix. (a) Sidebar menu, (b) heatmap plus dendrogram of the community matrix, (c) rarefaction curves of individual sites. \label{fig:fig1}](../fig/fig_1.jpg)

@@

![The GUI of divan after loading a trait matrix. (a) Sidebar menu, (b) selection of functional traits for analysis and plotting, (c) Principal Coordinate Analysis (PCoA) inputs, (d) biplot of species and functional traits plus density kernel surface.\label{fig:fig2}](../fig/fig_2.jpg)

@@

# Acknowledgements
FXP acknowledges financial support by Consejo Nacional de Investigaciones Científicas y Técnicas (Project PIBAA 28720210100513CO). Federico Riva, Gianluigi Ottaviani, and Stefano Mammola provided thoughtful comments on this manuscript.
